DATA 624 Homework 6

### 2020-03-18 DATA624/HW6.Rmd
More work on HW 6

```{r setup, echo=FALSE, cache=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA, message=FALSE, warning=FALSE)
library(tidyverse)
library(fpp2)
library(kableExtra)
library(gridExtra)
library(readxl)
library(urca)
options(scipen=999)
```

@@

**It needed to be differenced by `r ndiffs(usnetelec)`.  This is further confirmed using the KPSS Unit Root test below:**

```{r}
usnetelec %>% diff() %>% ur.kpss() %>% summary()
```

@@

```{r}
bc_usgdp %>% diff() %>% ur.kpss() %>% summary()
```

@@

@@

@@

@@

@@

@@

@@

>>>>

```{r setup, echo=FALSE, cache=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA, message=FALSE, warning=FALSE)
library(tidyverse)
library(fpp2)
library(kableExtra)
library(gridExtra)
library(readxl)
library(tseries)
options(scipen=999)
```

@@

**It needed to be differenced by `r ndiffs(usnetelec)`, or a first order difference.  Now to check if the data is stationary.**

```{r}
is_stationary <- function(data){
  results <- kpss.test(data)
  if (results$p.value > 0.05){
    "Data IS Stationary"
  } else {
    "Data IS NOT Stationary"
  }
}

cat(is_stationary(diff(usnetelec, ndiffs(usnetelec))))
```

**The p-value of 0.36 indicates the data are stationary.**

@@

**The Box Cox transformation with a lambda of `r round(usgdp_lambda,2)` and a differencing of `r ndiffs(bc_usgdp)`.**

```{r}
cat(is_stationary(diff(bc_usgdp, ndiffs(bc_usgdp))))
```

@@

**This has the spike in copper prices that happened late in the the 2000's.**

@@

**The Box Cox transformation with a lambda of `r round(mcopper_lambda,2)` and a differencing of `r ndiffs(bc_mcopper)`.**

```{r}
cat(is_stationary(diff(bc_mcopper, ndiffs(bc_mcopper))))
```

@@

**The variance is not constant so this series needs a Box-Cox transformation and differencing to be stationary.**

@@

**The Box Cox transformation with a lambda of `r round(enplanements_lambda,2)` and a differencing of `r ndiffs(bc_enplanements)` (1st order).**

```{r}
cat(is_stationary(diff(bc_enplanements, ndiffs(bc_enplanements))))
```

@@

**This series also exhibits an increasing variance and trend so Box-Cox and differencing will be needed.**

@@

**The Box Cox transformation had a lambda of `r round(visitors_lambda,2)` and a differencing of `r ndiffs(bc_visitors)` (1st order).**

```{r}
cat(is_stationary(diff(bc_visitors, ndiffs(bc_visitors))))
```

@@

```{r}
retaildata <- read_excel("retail.xlsx", skip = 1)
retail <- ts(retaildata[, "A3349873A"], frequency = 12, start = c(1982, 4))
retail_lambda <- BoxCox.lambda(retail)
bc_retail <- BoxCox(retail, lambda = retail_lambda)
ggtsplot(diff(bc_retail, ndiffs(bc_retail)), paste0("Differenced Monthly Retail Sales (lag=", ndiffs(bc_retail), ", lambda=",round(retail_lambda,2),")"))
```

**The data is differenced with a first order difference and adjusted with a Box Cox transformation with a lambda of `r round(retail_lambda,2)`.  The result:**

```{r}
cat(is_stationary(diff(bc_retail, ndiffs(bc_retail))))
```
